Downstream analysis: A pipeline to analyse time-course gene expression data

### 2019-05-06 scripts/04_downstream_analysis.Rmd
04_downstream_analysis.Rmd needs to import topGO

```{r}
gene_names = row.names(labels)
gene_names = gene_names[!is.na(labels)]
labels = labels[!is.na(labels)]
```

@@

`biomaRt` queries results a matrix with two named columns of gene names and GO
term ID. **FIXME** matrix or data.frame??

```{r go_to_gene_mapping, results="hide", message=FALSE}
# FIXME move this to the package
genes = biomaRt::getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

@@

```{r go_term_enrichment, results="hide", message=FALSE}
go_terms_enriched = find_enriched_go_terms(
    scores,
    13,
    gene_id_go_mapping, ontology="BP")
```

go_terms_enriched = go_terms_enriched[
    order(go_terms_enriched[, "resultFisher_padj"]), ]

kable(go_terms_enriched, "html", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```

>>>>

```{r}
gene_names = row.names(labels)
gene_names = gene_names[!is.na(labels)]
labels = as.vector(labels[!is.na(labels)])
names(labels) = gene_names
```

@@

`biomaRt` queries results a matrix with two named columns of gene names and GO
term ID.

```{r go_to_gene_mapping, results="hide", message=FALSE}
library(topGO)
#source("GO_terms_analysis.R")
genes = biomaRt::getBM(attributes=c("go_id", "refseq_mrna"),
	      values=gene_names,
	      filters="refseq_mrna",
	      mart=ensembl)

@@

```{r go_term_enrichment, results="hide", message=FALSE}
assignments = labels == cluster

go_terms_enriched = find_enriched_go_terms(
    assignments,
    gene_id_go_mapping, ontology="BP")
```
